---
title: "CVGA"
author: "Jeff Plambeck"
date: "1/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)

#setting directory
setwd("C:/Users/mnwadiugwu/Box/Martin/CVGA-2")

#loading bins from TWPH
load("Filtered_A1C_TIme_3Point_V4_Step4.bin")

#filter rows with at least 5 A1C's
filter <- df$Seq_Count >= 5
All.CVGA <- df[filter,]


#initialize vectors to zero
vMin <-c() # vector of minimums
vMax <- c() # vector of maximums
vUPI <- c() # vector of UPI's associated with the min and max
vA1Ctrend <- c()
vCV <- c()
vMean <- c()
vSD <- c()
#Cycle through All.CVGA and extract information needed:
for(n in 1:nrow(All.CVGA)){
  vA1c <-unlist(All.CVGA$A1c[n][[1]])
  vA1c <- as.double(vA1c)
  #Find the minimum from the last 5 A1C's
  Min <- min(vA1c[(length(vA1c)-4):length(vA1c)]) #Extract individual Min
  vMin <- c(vMin, paste(Min, sep= ","))           #Add individual min to vector
  
 
  
  #Find the Maximum from the last 5 A1C's
  Max <- max(vA1c[(length(vA1c)-4):length(vA1c)])
  mean <- mean(vA1c[(length(vA1c)-4):length(vA1c)])
  std_dev <- sd(vA1c[(length(vA1c)-4):length(vA1c)])
  cv <- (std_dev/mean) * 100
  #last5 <-   vA1c[(length(vA1c)-4):length(vA1c)]

  vMax <- c(vMax, paste(Max, sep= ","))
  #where are the maixmum and  minimum
  min.pos <- which.min(vA1c[(length(vA1c)-4):length(vA1c)])
  max.pos <- which.max(vA1c[(length(vA1c)-4):length(vA1c)])
  if(max.pos > min.pos) {
    aicTrend = "Increased"
  }else {
    aicTrend = "Decreased"
  }
  #Extract the UPI associated with max and min
  UPI <- All.CVGA$UID[n]
  vUPI <- c(vUPI, paste(UPI, sep= ","))
  vA1Ctrend <- c(vA1Ctrend, aicTrend)
  vMean <- c(vMean,mean)
  vCV <- c(vCV, cv)
  vSD <- c(vSD, std_dev)
}

#column bind the three created vectors into a dataframe
vMin <- as.numeric(vMin)
vMax <- as.numeric(vMax)

All.CVGA.Filtered <- data.frame(vUPI, vMin, vMax, vA1Ctrend, vMean, vSD, vCV,stringsAsFactors = F)
colnames(All.CVGA.Filtered) <- c("UPI", "Min", "Max","aicTrend", "mean","sd","cv")
Amplitude <- All.CVGA.Filtered$Max - All.CVGA.Filtered$Min
All.CVGA.Filtered <- cbind(All.CVGA.Filtered,Amplitude)
typeof(All.CVGA.Filtered)


All.Amplitude <- data.frame(Amplitude)

All.CVGA.Filtered$Min <- unlist(as.numeric(All.CVGA.Filtered$Min))
All.CVGA.Filtered$Max <- unlist(as.numeric(All.CVGA.Filtered$Max))

#reading daignosis data

Diagnosis <- read.table(file="Diagnosis_ICD10.csv",sep=",",header=T,stringsAsFactors = F)
Diagnosis.combined <- aggregate(Diagnosis$three_digit, by=list(Diagnosis$UPI), paste)
index <- match(All.CVGA.Filtered$UPI,Diagnosis.combined$Group.1)
dc <- Diagnosis.combined[index,2]
diagnosis <- unlist(lapply(dc,function(x) {paste(x,collapse=",")}))
diagnosis <- gsub(",NA","",gsub("NA,","",diagnosis))
diagnosis.count <- unlist(lapply(dc,function(x) {length(unique(x))}))
All.CVGA.Filtered.diagnosis <- cbind(All.CVGA.Filtered, diagnosis, diagnosis.count)

#reading drug class data
MedCode <- read.csv(file="UniqueDrugClass.csv",sep=",",header=T,stringsAsFactors = F)
MedCode1 <- aggregate(MedCode$X4.digit, by=list(MedCode$`ï..UPI`), paste)

index <- match(All.CVGA.Filtered$UPI, MedCode$`ï..UPI`)
mc <- MedCode1[index,2]

medcode <- unlist(lapply(mc,function(x) {paste(x,collapse=",")}))
medcode <- gsub(",NA","",gsub("NA,","",medcode))
medcode.count <- unlist(lapply(mc,function(x) {length(unique(x))}))

All.CVGA.Filtered.diagnosis.medcode <- cbind(All.CVGA.Filtered.diagnosis, medcode, medcode.count)


upc.diagnosis <- All.CVGA.Filtered.diagnosis.medcode[,c("UPI","diagnosis")]
diagnosis.uniq <- lapply(strsplit(as.character(upc.diagnosis$diagnosis),split=","),unique)
long.table <- NULL
for (i in 1:length(diagnosis.uniq)) {
  d <- diagnosis.uniq[[i]]
  if(length(d) > 0) {
    long.table <- rbind(long.table,cbind(upc.diagnosis$UPI[i],d))
  }
}
colnames(long.table) <- c("UPI","diagnosis_code")
length(unique(long.table[,1]))



library(reshape2)
wide.table <- dcast(data.frame(long.table),UPI ~diagnosis_code)
rownames(wide.table) <- wide.table[,1]
wide.table <- wide.table[,-1]
wide.table[!is.na(wide.table)] <- 1

wide.table[is.na(wide.table)] <- 0

  
write.csv(wide.table,"upi_diagnosis_wide.table.csv")

smaller.wide <- data.frame(wide.table[match(as.character(All.CVGA.Filtered.diagnosis.medcode$UPI),rownames(wide.table)),])
smaller.wide <- smaller.wide[-grep("NA",rownames(smaller.wide)),]
                        
cov <- All.CVGA.Filtered.diagnosis.medcode[match(rownames(smaller.wide),All.CVGA.Filtered.diagnosis.medcode[,1]), c(7)]
print(summary(cov))
smaller.wide <- cbind(smaller.wide, cov)
smaller.wide2 <- smaller.wide[,-1]

write.csv(smaller.wide,"DiagnosisAndCV.csv")
write.csv(smaller.wide2,"DiagnosisAndCV2.csv")




##Finding intersection between list of medcodes with the existing one

my.list <- c("N95", "R10", "R09", "F41", "M54", "R21", "B37", "E88", "R51", "H66", "J01", "F32", "R11", "D48", "R05", "J06", "J30", "M25", "R79", "J32", "R07", "Z09", "N39", "K21", "R19", "R20")

diagnosis.list <- strsplit(as.character(All.CVGA.Filtered.diagnosis.medcode$diagnosis),split = ",")

my.intersect.diagnosis.list <- lapply(diagnosis.list, function(x) {intersect(my.list,x)} )
intersect.count <- unlist(lapply(my.intersect.diagnosis.list,length))
my.intersect.diagnosis.string <- unlist(lapply(my.intersect.diagnosis.list,function(x) {paste(x,collapse=",")}))
  


All.CVGA.Filtered.diagnosis.medcode <- cbind(All.CVGA.Filtered.diagnosis.medcode,intersect.count)
All.CVGA.Filtered.diagnosis.medcode <- cbind(All.CVGA.Filtered.diagnosis.medcode, my.intersect.diagnosis.string)


my.list2 <- c("I73", "R26", "R60", "M20", "B35", "I83", "I48", "D64", "I25", "I50", "Z91")

diagnosis.list1 <- strsplit(as.character(All.CVGA.Filtered.diagnosis.medcode$diagnosis),split = ",")

my.intersect.diagnosis.list1 <- lapply(diagnosis.list1, function(x) {intersect(my.list2,x)} )
intersect.count1 <- unlist(lapply(my.intersect.diagnosis.list1,length))
my.intersect.diagnosis.string1 <- unlist(lapply(my.intersect.diagnosis.list1,function(x) {paste(x,collapse=",")}))
  


All.CVGA.Filtered.diagnosis.medcode <- cbind(All.CVGA.Filtered.diagnosis.medcode,intersect.count1)
All.CVGA.Filtered.diagnosis.medcode <- cbind(All.CVGA.Filtered.diagnosis.medcode, my.intersect.diagnosis.string1)

my.list3 <- c("Z02", "I12", "I11", "T41", "E28", "Z11")

diagnosis.list2 <- strsplit(as.character(All.CVGA.Filtered.diagnosis.medcode$diagnosis),split = ",")

my.intersect.diagnosis.list2 <- lapply(diagnosis.list2, function(x) {intersect(my.list3,x)} )
intersect.count2 <- unlist(lapply(my.intersect.diagnosis.list2,length))
my.intersect.diagnosis.string2 <- unlist(lapply(my.intersect.diagnosis.list2,function(x) {paste(x,collapse=",")}))
  


All.CVGA.Filtered.diagnosis.medcode <- cbind(All.CVGA.Filtered.diagnosis.medcode,intersect.count2)
All.CVGA.Filtered.diagnosis.medcode <- cbind(All.CVGA.Filtered.diagnosis.medcode, my.intersect.diagnosis.string2)


my.list4 <- c("I10", "E65", "E67", "E68", "E78", "I12", "I13", "N18", "I25")

diagnosis.list3 <- strsplit(as.character(All.CVGA.Filtered.diagnosis.medcode$diagnosis),split = ",")

my.intersect.diagnosis.list3 <- lapply(diagnosis.list3, function(x) {intersect(my.list4,x)} )
intersect.count3 <- unlist(lapply(my.intersect.diagnosis.list3,length))
my.intersect.diagnosis.string3 <- unlist(lapply(my.intersect.diagnosis.list3,function(x) {paste(x,collapse=",")}))
  

All.CVGA.Filtered.diagnosis.medcode <- cbind(All.CVGA.Filtered.diagnosis.medcode,intersect.count3)
All.CVGA.Filtered.diagnosis.medcode <- cbind(All.CVGA.Filtered.diagnosis.medcode, my.intersect.diagnosis.string3)

#Filtering data based on %CV range

Filter2 <- All.CVGA.Filtered.diagnosis.medcode[All.CVGA.Filtered.diagnosis.medcode$Max<= 7,]
Best2<-Filter2


Filter3 <- All.CVGA.Filtered.diagnosis.medcode[All.CVGA.Filtered.diagnosis.medcode$Max >= 7,]
Worst<-Filter3

cv2 <- Worst[Worst$cv>= 20,]
Worstcv2 <- cv2

cv3 <- All.CVGA.Filtered.diagnosis.medcode[All.CVGA.Filtered.diagnosis.medcode$cv<= 10,]
AllCV1 <- cv3

cv4 <- All.CVGA.Filtered.diagnosis.medcode[All.CVGA.Filtered.diagnosis.medcode$cv > 10 & All.CVGA.Filtered.diagnosis.medcode$cv <=20,]
AllCV2 <- cv4

cv5 <- All.CVGA.Filtered.diagnosis.medcode[All.CVGA.Filtered.diagnosis.medcode$cv > 20 & All.CVGA.Filtered.diagnosis.medcode$cv <=30,]
AllCV3 <- cv5

cv6 <- All.CVGA.Filtered.diagnosis.medcode[All.CVGA.Filtered.diagnosis.medcode$cv > 30,]
AllCV4 <- cv6


#creating diagnosis dataframe
colnames(All.CVGA.Filtered)[9]<- "diagnosis"

#writing data to file based on %CV range

write.csv(Worst, file="Worst.csv",quote=FALSE,row.names = FALSE)

write.csv(Best2, file="Best2.csv",quote=FALSE,row.names = FALSE)
write.csv(All.CVGA.Filtered, file="All.CVGA.Filtered.csv",quote=FALSE,row.names = FALSE)
write.csv(Worstcv2, file="Worstcv2",quote=FALSE,row.names = FALSE)
write.csv(All.CVGA.Filtered.diagnosis, file="All.CVGA.Filtered.diagnosis",quote=FALSE,row.names = FALSE)


```

### Review the data: Minimum

```{r, echo = TRUE}
summary(All.CVGA.Filtered$Min)
ggplot() + geom_histogram(data=All.CVGA.Filtered, aes(x=Min))

```

```{r, echo = TRUE}
summary(All.CVGA.Filtered$Max)
ggplot() + geom_histogram(data=All.CVGA.Filtered, aes(x=Max))

```
## Plot VGA Graph: starting with the background and moving to the foreground

### Background squares using geom_rect, Unknown boundaries but here is how you would define them
Check fill is in correct position before moving on

```{r, echo=TRUE}
#Set Boundary definitions 1 for each square (9)
#First Level
a=data.frame(x1=1, x2=2, y1=4, y2=5, t='yellow', r="a") #bottom right

plot1 <- ggplot() +
  scale_x_reverse(limits =c(4,1),breaks = seq(from=4, to=1, by=-1), name="Min") + 
  scale_y_continuous(limits =c(4,7), breaks = seq(from=4, to=7, by=1), name="Max") +
  geom_rect(show.legend = FALSE)

#Set up background rectangle sizes,remove legend, add text to indicate what the colors mean
plot1 <- plot1 + 
  geom_rect(data=a, 
            mapping=aes(xmin=-Inf, xmax=x2, ymin=-Inf, ymax=y2), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 1.5, y = 4.5, label = "a"), size =3, color = "Black") 

print(plot1)
```

Fill in the rest of the row

```{r, echo=TRUE}
#Set Boundary definitions 1 for each square (9)
#First Level
a=data.frame(x1=1, x2=2, y1=4, y2=5, t='yellow', r="a") #bottom right
b=data.frame(x1=2, x2=3, y1=4, y2=5, t='b', r="b") #bottom middle
c=data.frame(x1=3, x2=4, y1=4, y2=5, t='c', r="c") #bottom left

plot1 <- ggplot() +
  scale_x_reverse(limits =c(4,1),breaks = seq(from=4, to=1, by=-1), name="Min") + 
  scale_y_continuous(limits =c(4,7), breaks = seq(from=4, to=7, by=1), name="Max") +
  geom_rect(show.legend = FALSE)

#Set up background rectangle sizes,remove legend, add text to indicate what the colors mean
plot1 <- plot1 + 
  geom_rect(data=a, 
            mapping=aes(xmin=-Inf, xmax=x2, ymin=-Inf, ymax=y2), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 1.5, y = 4.5, label = "a"), size =3, color = "Black") +
  geom_rect(data=b, 
            mapping=aes(xmin=x1, xmax=x2, ymin=-Inf, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 2.5, y = 4.5, label = "b"), size =3, color = "Black") +
  geom_rect(data=c, 
            mapping=aes(xmin=x1, xmax=Inf, ymin=-Inf, ymax=y2), 
            color="black",
            fill = 'dark green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 3.5, y = 4.5, label = "c"), size =3, color = "Black") 

print(plot1)
```

Build the rest of the background

```{r, echo=TRUE}
#Set Boundary definitions 1 for each square (9)
#First Level
a=data.frame(x1=1, x2=2, y1=4, y2=5, t='yellow', r="a") #bottom right
b=data.frame(x1=2, x2=3, y1=4, y2=5, t='b', r="b") #bottom middle
c=data.frame(x1=3, x2=4, y1=4, y2=5, t='c', r="c") #bottom left
#Second Level
d=data.frame(x1=1, x2=2, y1=5, y2=6, t='d', r="d") #middle right
e=data.frame(x1=2, x2=3, y1=5, y2=6, t='e', r="e") #middle middle
f=data.frame(x1=3, x2=4, y1=5, y2=6, t='f', r="f") #middle left
#Third Level
g=data.frame(x1=1, x2=2, y1=6, y2=7, t='g', r="g") #middle right
h=data.frame(x1=2, x2=3, y1=6, y2=7, t='h', r="h") #middle middle
i=data.frame(x1=3, x2=4, y1=6, y2=7, t='i', r="i") #middle left

plot1 <- ggplot() +
  scale_x_reverse(limits =c(4,1),breaks = seq(from=4, to=1, by=-1), name="Min") + 
  scale_y_continuous(limits =c(4,7), breaks = seq(from=4, to=7, by=1), name="Max") +
  geom_rect(show.legend = FALSE)

#Set up background rectangle sizes,remove legend, add text to indicate what the colors mean
plot1 <- plot1 + 
  geom_rect(data=a, 
            mapping=aes(xmin=-Inf, xmax=x2, ymin=-Inf, ymax=y2), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 1.5, y = 4.5, label = "a"), size =3, color = "Black") +
   geom_rect(data=b, 
            mapping=aes(xmin=x1, xmax=x2, ymin=-Inf, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 2.5, y = 4.5, label = "b"), size =3, color = "Black") +
  geom_rect(data=c, 
            mapping=aes(xmin=x1, xmax=Inf, ymin=-Inf, ymax=y2), 
            color="black",
            fill = 'dark green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 3.5, y = 4.5, label = "c"), size =3, color = "Black")+ 
  geom_rect(data=d, 
            mapping=aes(xmin=-Inf, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'orange',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 1.5, y = 5.5, label = "d"), size =3, color = "Black") +
  geom_rect(data=e, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 2.5, y = 5.5, label = "e"), size =3, color = "Black") +
  geom_rect(data=f, 
            mapping=aes(xmin=x1, xmax=Inf, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 3.5, y = 5.5, label = "f"), size =3, color = "Black")+
  geom_rect(data=g, 
            mapping=aes(xmin=-Inf, xmax=x2, ymin=y1, ymax=Inf), 
            color="black",
            fill = 'red',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 1.5, y = 6.5, label = "g"), size =3, color = "Black") +
  geom_rect(data=h, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=Inf), 
            color="black",
            fill = 'orange',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 2.5, y = 6.5, label = "h"), size =3, color = "Black") +
  
  geom_rect(data=i, 
            mapping=aes(xmin=x1, xmax=Inf, ymin=y1, ymax=Inf), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 3.5, y = 6.5, label = "i"), size =3, color = "Black") 

print(plot1)
```


If you want boundaries square instead

```{r, echo=TRUE}
#Set Boundary definitions 1 for each square (9)
#First Level
a=data.frame(x1=1, x2=2, y1=4, y2=5, t='yellow', r="a") #bottom right
b=data.frame(x1=2, x2=3, y1=4, y2=5, t='b', r="b") #bottom middle
c=data.frame(x1=3, x2=4, y1=4, y2=5, t='c', r="c") #bottom left
#Second Level
d=data.frame(x1=1, x2=2, y1=5, y2=6, t='d', r="d") #middle right
e=data.frame(x1=2, x2=3, y1=5, y2=6, t='e', r="e") #middle middle
f=data.frame(x1=3, x2=4, y1=5, y2=6, t='f', r="f") #middle left
#Third Level
g=data.frame(x1=1, x2=2, y1=6, y2=7, t='g', r="g") #middle right
h=data.frame(x1=2, x2=3, y1=6, y2=7, t='h', r="h") #middle middle
i=data.frame(x1=3, x2=4, y1=6, y2=7, t='i', r="i") #middle left

plot1 <- ggplot() +
  scale_x_reverse(limits =c(4,1),breaks = seq(from=4, to=1, by=-1), name="Min") + 
  scale_y_continuous(limits =c(4,7), breaks = seq(from=4, to=7, by=1), name="Max") +
  geom_rect(show.legend = FALSE)

#Set up background rectangle sizes,remove legend, add text to indicate what the colors mean
plot1 <- plot1 + 
  geom_rect(data=a, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 1.5, y = 4.5, label = "a"), size =3, color = "Black") +
   geom_rect(data=b, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 2.5, y = 4.5, label = "b"), size =3, color = "Black") +
  geom_rect(data=c, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'dark green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 3.5, y = 4.5, label = "c"), size =3, color = "Black")+ 
  geom_rect(data=d, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'orange',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 1.5, y = 5.5, label = "d"), size =3, color = "Black") +
  geom_rect(data=e, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 2.5, y = 5.5, label = "e"), size =3, color = "Black") +
  geom_rect(data=f, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 3.5, y = 5.5, label = "f"), size =3, color = "Black")+
  geom_rect(data=g, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'red',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 1.5, y = 6.5, label = "g"), size =3, color = "Black") +
  geom_rect(data=h, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'orange',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 2.5, y = 6.5, label = "h"), size =3, color = "Black") +
  
  geom_rect(data=i, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE) + 
  geom_text(aes(x = 3.5, y = 6.5, label = "i"), size =3, color = "Black") 

print(plot1)
```


Change boundaries and axes to fit data

```{r, echo=TRUE}
#Set Boundary definitions 1 for each square (9)
#First Level
a=data.frame(x1=4, x2=5, y1=7, y2=9, t='a', r="a") #bottom right
b=data.frame(x1=5, x2=6, y1=7, y2=9, t='b', r="b") #bottom middle
c=data.frame(x1=6, x2=7, y1=7, y2=9, t='c', r="c") #bottom left
#Second Level
d=data.frame(x1=4, x2=5, y1=9, y2=11, t='d', r="d") #middle right
e=data.frame(x1=5, x2=6, y1=9, y2=11, t='e', r="e") #middle middle
f=data.frame(x1=6, x2=7, y1=9, y2=11, t='f', r="f") #middle left
#Third Level
g=data.frame(x1=4, x2=5, y1=11, y2=14, t='g', r="g") #middle right
h=data.frame(x1=5, x2=6, y1=11, y2=14, t='h', r="h") #middle middle
i=data.frame(x1=6, x2=7, y1=11, y2=14, t='i', r="i") #middle left

plot1 <- ggplot() +
  scale_x_reverse(limits =c(7,4),breaks = seq(from=7, to=4, by=-1), name="Min") + 
  scale_y_continuous(limits =c(7,14), breaks = seq(from=7, to=14, by=2), name="Max") +
  geom_rect(show.legend = FALSE)

#Set up background rectangle sizes,remove legend, add text to indicate what the colors mean
plot1 <- plot1 + 
  geom_rect(data=a, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 1.5, y = 4.5, label = "a"), size =3, color = "Black") +
   geom_rect(data=b, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 2.5, y = 4.5, label = "b"), size =3, color = "Black") +
  geom_rect(data=c, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'dark green',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 3.5, y = 4.5, label = "c"), size =3, color = "Black")+ 
  geom_rect(data=d, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'orange',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 1.5, y = 5.5, label = "d"), size =3, color = "Black") +
  geom_rect(data=e, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 2.5, y = 5.5, label = "e"), size =3, color = "Black") +
  geom_rect(data=f, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 3.5, y = 5.5, label = "f"), size =3, color = "Black")+
  geom_rect(data=g, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'red',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 1.5, y = 6.5, label = "g"), size =3, color = "Black") +
  geom_rect(data=h, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'orange',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 2.5, y = 6.5, label = "h"), size =3, color = "Black") +
  
  geom_rect(data=i, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE)
  #geom_text(aes(x = 3.5, y = 6.5, label = "i"), size =3, color = "Black") 

print(plot1)
```


Add Data over top

```{r, echo=TRUE}
#Set Boundary definitions 1 for each square (9)
#First Level
a=data.frame(x1=4.0, x2=7.89, y1=4.0, y2=7.89, t='a', r="a") #bottom right
b=data.frame(x1=7.89, x2=12.08, y1=4.0, y2=7.89, t='b', r="b") #bottom middle
c=data.frame(x1=12.08, x2=15.0, y1=4.0, y2=7.89, t='c', r="c") #bottom left
#Second Level
d=data.frame(x1=4.0, x2=7.89, y1=7.89, y2=12.08, t='d', r="d") #middle right
e=data.frame(x1=7.89, x2=12.08, y1=7.89, y2=12.08, t='e', r="e") #middle middle
f=data.frame(x1=12.08, x2=15.0, y1=7.89, y2=12.08, t='f', r="f") #middle left
#Third Level
g=data.frame(x1=4.0, x2=7.89, y1=12.08, y2=15.0, t='g', r="g") #middle right
h=data.frame(x1=7.89, x2=12.08, y1=12.08, y2=15.0, t='h', r="h") #middle middle
i=data.frame(x1=12.08, x2=15.0, y1=12.08, y2=15.0, t='i', r="i") #middle left

plot1 <- ggplot() +
  scale_x_reverse(limits =c(15,3),breaks = seq(from=15, to=4, by=-5), name="Min") + 
  scale_y_continuous(limits =c(4,15), breaks = seq(from=4, to=15, by=5), name="Max") +
  geom_rect(show.legend = FALSE)

#Set up background rectangle sizes,remove legend, add text to indicate what the colors mean
plot1 <- plot1 + 
  geom_rect(data=a, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 1.5, y = 4.5, label = "a"), size =3, color = "Black") +
   geom_rect(data=b, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 2.5, y = 4.5, label = "b"), size =3, color = "Black") +
  geom_rect(data=c, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'dark green',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 3.5, y = 4.5, label = "c"), size =3, color = "Black")+ 
  geom_rect(data=d, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'orange',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 1.5, y = 5.5, label = "d"), size =3, color = "Black") +
  geom_rect(data=e, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 2.5, y = 5.5, label = "e"), size =3, color = "Black") +
  geom_rect(data=f, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'light green',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 3.5, y = 5.5, label = "f"), size =3, color = "Black")+
  geom_rect(data=g, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'red',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 1.5, y = 6.5, label = "g"), size =3, color = "Black") +
  geom_rect(data=h, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'orange',
            alpha=0.25,
            show.legend = FALSE) + 
  #geom_text(aes(x = 2.5, y = 6.5, label = "h"), size =3, color = "Black") +
  
  geom_rect(data=i, 
            mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), 
            color="black",
            fill = 'yellow',
            alpha=0.25,
            show.legend = FALSE) +
  #geom_text(aes(x = 3.5, y = 6.5, label = "i"), size =3, color = "Black") 
  
  geom_point(data=All.CVGA.Filtered, aes(x=Min, y=Max, shape=vA1Ctrend, color =vA1Ctrend, fill="blue", alpha=0)) 

print(plot1)
```

You can see a lot of data gets kicked out with this configuration. Im going to let you play with the boundaries and the shape sizes but I am not sure how to overcome the high amount of missing data.

```{r, echo=TRUE}

plot2 <-  ggplot() + geom_point(data=All.CVGA.Filtered, aes(x=Min, y=Max))

print(plot2)
```

